Informative Autonomous Sampling of Oceanographic Variables Using Joint Excursion Sets

### 2020-04-23 ans_to_reviewers/answers-to-reviewers.tex

\newcounter{reviewer}
\def\reply{\textbf{Reviewer query}}
\def\action{\textbf{Action taken}}

\newlist{answers}{enumerate}{10}
\setlist[answers]{leftmargin=*, label=\arabic{reviewer}.\arabic*}

\newcommand{\edcomment}[1]{{\color{green}{\{Editor: #1\}}}}
\newcommand{\frevcomment}[1]{{\color{blue}{\{Rev 1: #1\}}}}
\newcommand{\srevcomment}[1]{{\color{red}{\{Rev 2: #1\}}}}
\newcommand{\trevcomment}[1]{{\color{violet}{\{Rev 3: #1\}}}}

\usepackage{amsthm,amsmath,natbib}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}

@@

\action: Our actions

\item{Specific comments}\label{q11}

\reply: See the numbered list below:
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]

\item[1.1.1] “joint excursion sets” in the title would be a turnoff for most statisticians. Having read the paper pretty carefully I still am not sure why they are so labelled.\par
\action: Our actions
\vspace{1em}

\item[1.1.2] Why on page 13 were those particular values chosen for the means $\mu$? Would a different choice have made a difference?\par
\action: Our actions
\vspace{1em}

\item[1.1.3] I don’t think Figure 3 conveys too much additional benefit and eliminating it for space might be considered.\par
\action: Our actions
\vspace{1em}

\item[1.1.4] Why are the ES’s called ”excursion sets? Why excursion probabilities?\par
\action: Our actions
\vspace{1em}

\item[1.1.5] I did not spot a definition for the “waypoint graph” a phrase used several times in the paper. Again points to the need to identify the audience. I doubt that most statisticians would know that phrase.\par
\action: Our actions
\vspace{1em}

\item[1.1.6] In statistics journals, random variables are commonly labelled by Roman characters e.g. Z, parameters in Greek e.g. $\xi$. I realize that in other scientific domains that distinction is not always made but I do recommend the change if the paper is to appear in a stats journal.\par 
\action: Our actions
\vspace{1em}

\item[1.1.7] There is not much of novelty in the Gaussian Process theory used in the paper- its pretty much standard. I suggest that the derivations stated in detail be summarized by just the results. Statisticians will know these things and users will not care.\par
\action: Our actions
\vspace{1em}

@@

\begin{answers}
\item{Major comment 1 - Details on AUVs}\label{q12}

\reply: I know very little about the AUVs you discuss, and I suspect many of your readers will be in a similar position. Additional contextual information would be helpful

\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]

\item[2.1.1] What sort of onboard computing do they have? It may not be something like an Intel 2.1 GHz, 4-thread processor, but a more informative description of something most readers relate to would be helpful. Similar information related to RAM and hard drive space would be helpful. What are the computational limits of these machines?\par
\action: Our actions
\vspace{1em}

\item[2.1.2] How long do the AUVs typically explore in one go? Is there a minimum/maximum time?\par 
\action: Our actions
\vspace{1em}

\item[2.1.3] What kind of movements can the AUVs make? Chess-like moves (horizontal, vertical, diagonal)?\par  
\action: Our actions
\vspace{1em}

\item[2.1.4] Is there a minimum/maximum number of points you want to sample?\par
\action: Our actions
\vspace{1em}

\item[2.1.5] What is the size of the grid that is typically considered? i.e., what is a typical value of $n$ in Eq.(9)?\par 
\action: Our actions
\vspace{1em}

\item[2.1.6] Does the AUV use a selection algorithm from the very beginning or is there a minimum number of initial measurements that are made before the optimization algorithm begins?\par
\action: Our actions
\vspace{1em}

@@

\action: Our actions

\item{Minor comments}\label{q26}

\reply: \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]

\item[2.15.1] “closed-form” is sometimes written as “closed form” (e.g., p. 7, p. 18)

\item[2.15.2] p. 9, `1s` should be ‘1s’. Similar for 0s.

\item[2.15.3] p. 15, my manuscript has -on where to sample-, which is an unusual use of dashes.

@@

\item{Comments to the Author}\label{q30}

\reply: Specific comments:

\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]

\item[3.1.1] General: The inferential problem considered is the paper is that of estimating the “boundary”
of a plume. However, the authors never define exactly what a “boundary” is. Such a definition
should be provided, as well as some discussion of why determining the location of a boundary
is so important. Why is it not sufficient to create a map of predictions (with an accompanying
map of prediction error variances) for the variable(s) under study throughout the region of
interest (a problem for which there is a huge literature on sampling design)?\par
\action: Our actions
\vspace{1em}

\item[3.1.2] Page 8, second paragraph of Section 4.1: The assumptions of separability and isotropy, and even stationarity, are not really necessary for the methodological development of Sections 4–6.
I suggest that you wait to make these assumptions until you get to the simulation studies and
example.\par
\action: Our actions
\vspace{1em}

\item[3.1.3] Page 9, second paragraph of Section 4.2: It has been assumed here that the measurement
errors for temperature and salinity at any given location are uncorrelated. Is this a reasonable
assumption? This could easily be checked by taking replicate measurements at each site.\par
\action: Our actions
\vspace{1em}

\item[3.1.4] General: Related to the previous point, I do not understand why sampling locations are being restricted to a regular grid. In fact, it seems unwise because it is well known (see, for example, Chapters 9 and 22 of Handbook of Environmental and Ecological Statistics, 2019, CRC Press)
that the quality of inferences for spatial fields can be improved substantially by taking some
observations very close to others.\par
\action: Our actions
\vspace{1em}

\item[3.1.5] Page 13, last line: Specifically, what was the design? We aren’t even told what the sample size ($n_y$) was used in these calculations.\par
\action: Our actions
\vspace{1em}

\item[3.1.6] Page 18, first paragraph of Section 7.1: The numerical values of the regression parameters given here are not meaningful without knowing the units of “West.”\par
\action: Our actions
\vspace{1em}

\item[3.1.7] Page 24, first paragraph of Fig. 8: Please define “the modeled quadratic form of the residuals” more precisely. Perhaps a mathematical expression is needed for clarity.\par
\action: Our actions
\vspace{1em}

@@

\end{itemize}

\item{Minor comments to the Author}\label{q31}

\reply: 
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]

\item[3.2.1] Page 3, line 19: Change “bi-variate” to “bivariate”. The same change is needed on the next-
to-last line of Page 12.

\item[3.2.2] Page 9, three lines after (10): I presume that all off-diagonal elements of R are zeros, but this
should be stated explicitly.

\item[3.2.3] Page 19, fourth line from bottom: Change ``as also" to ``as well as"

\item[3.2.4] Page 30, second and third references listed: ``et al." is listed after the authors’ names for each
of these two references, but actually there are no additional authors beyond the two listed.

@@

\end{itemize}

\action: 
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]

\item[3.2.1] we have changed this in the text - page 3 and 12.

\item[3.2.2] we have added a statement on page 9: $\bR$ contains \edcomment{zeroes except on the diagonal entries, which are set to $r^2_T$ and $r^2_S$, holding the measurement error variances of temperature and salinity observations}.

\item[3.2.3] we have changed this in the text - page 19.

\item[3.2.4] we have made this change to the citations \cite{genton2015cross} and \cite{french2016credible} - page 30.

### 2020-04-23 main_new.tex
Updated with Ans-to-Rev
Started answering and reformatted the answers into bullets

The remainder of this paper is organized as follows: Section
\ref{sec:bg} provides select background on ocean sampling; Section
\ref{sec:ESEP} defines ESs, EPs, and the design criteria of IBV;
Section \ref{sec:GP_EP} sets up the required statistical modeling
assumptions of the bi-variate GPs for temperature and salinity;
Section \ref{sec:sur} builds on these assumptions when deriving the
analytical derivation of the design criteria; Section
\ref{sec:heuristics} extends these results and present heuristics for
adaptive sampling; Section \ref{sec:simulations}
discusses properties of the methods in simulation studies. Section
\ref{sec:case_study} demonstrates the methodology used in field work
characterizing a river plume; and Section \ref{sec:concl_disc}
contains a summary and a discussion of future work.

@@

We denote the data at $n_y$ locations by
$\by=(y_{T,1},y_{S,1},\ldots,y_{T,n_y},y_{S,n_y})^t$, representing the
temperature and salinity measurements gathered at the first stage of
nodes in the grid. The conditional model for the data, given the true temperature
and salinity, is described by: 
\begin{equation}\label{likelihood}
\by | \bxi \sim N( \bG \bxi, \bR), %\pi(\by | \bxi)= \frac{1}{(2\pi)^{m}|\bR|^{\frac{1}{2}}}e^{-\frac{1}{2}(\by -\bG\bxi)^T\bR^{-1}(\by-\bG\bxi)},
\end{equation}
where $\bG$ is a $2n_y \times 2n$ matrix containing '$1$'s on the
measurement indices of the grid and '$0$' otherwise. The size
$2n_y \times 2n_y$ covariance matrix $\bR$ contains diagonal entries
$r^2_T$ and $r^2_S$ which are measurement error variances of
temperature and salinity observations.

@@

In our application domain with the variables temperature and salinity,
the solutions to the complex integral equations for the expected IBV
are reduced to calculating bi-variate and four-variate cumulative
distribution functions for Gaussian vectors. For the more general
case, one would be interested in $K$ random fields. In the ocean
sciences, the variables could include chlorophyll or other
bio-geochemical quantities in addition to temperature and salinity.

@@

The covariance is assumed to be stationary and separable for the two variables. 
The $2 \times 2$ pointwise covariance matrix is set to:
\begin{equation}\label{v0}
\bSigma(\bx)=\mbox{Var} 
\begin{bmatrix}
    \xi_T(\bx) \\
    \xi_S(\bx) 
    \end{bmatrix}=
\begin{bmatrix}
0.25^2 & 0.6 \cdot 0.25^2 \\
0.6 \cdot 0.25^2 & 0.25^2
\end{bmatrix}.
\end{equation}
The spatial correlation is of a Matern type \citep{Matern2013}:
\begin{equation}\label{v}
\small
\mbox{Corr} 
\left(
\begin{bmatrix}
    \xi_T(\bx) \\
    \xi_S(\bx) 
    \end{bmatrix},
    \begin{bmatrix}
    \xi_T(\bx') \\
    \xi_S(\bx') 
    \end{bmatrix}
    \right)
    = \begin{bmatrix}
1 & 0.6  \\
0.6  & 1
\end{bmatrix}(1+\phi h)\exp (-\phi h),
\end{equation}
where $h=\sqrt{||\bx-\bx'||^2}$ and $\phi=0.3$ indicates an effective correlation range of about $1200$ m. 
%Figure \ref{fig:stat_design} shows the contour lines for the EP for the reference. We notice the trend of increasing salinity and temperature to the west.  
One realization of the random fields representing salinity and
temperature is shown in Fig. \ref{fig:true_temp} and
\ref{fig:true_sal}. The true ES is a realization from this model as shown
in Fig. \ref{fig:ESet}.

@@

For a fixed survey length, a closed form expression for the expected IBV is available as in Eq. \eqref{sur}. However, for the sequential approaches this is not the
case. For comparison the properties are therefore evaluated using
Monte Carlo sampling over several replicates of realizations from the model while conducting simulated sequential surveys for each
one. Fig. \ref{fig:Eprob} shows the conditional EP, given data
gathered along the north-south survey lines in these figures. In the
Monte Carlo replicates, such results are repeatedly computed to
approximate the expected IBV. We also compare predictive performance
measured by root mean square error (RMSE) for temperature and salinity
estimates as also the variance reduction in these two variables. It is
important to note that the objective function used by the agent is
focused on reducing the expected IBV, but we nevertheless expect that
we will achieve good predictive performance for criteria such as RMSE
as well. Another non-statistical criteria that is important for
practical purposes is the computational time needed for the strategy,
as this will impact the performance for an embedded system.

>>>>

The remainder of this paper is organized as follows: Section
\ref{sec:bg} provides select background on ocean sampling; Section
\ref{sec:ESEP} defines ESs, EPs, and the design criteria of IBV;
Section \ref{sec:GP_EP} sets up the required statistical modeling
assumptions of the bivariate GPs for temperature and salinity;
Section \ref{sec:sur} builds on these assumptions when deriving the
analytical derivation of the design criteria; Section
\ref{sec:heuristics} extends these results and present heuristics for
adaptive sampling; Section \ref{sec:simulations}
discusses properties of the methods in simulation studies. Section
\ref{sec:case_study} demonstrates the methodology used in field work
characterizing a river plume; and Section \ref{sec:concl_disc}
contains a summary and a discussion of future work.

@@

We denote the data at $n_y$ locations by
$\by=(y_{T,1},y_{S,1},\ldots,y_{T,n_y},y_{S,n_y})^t$, representing the
temperature and salinity measurements gathered at the first stage of
nodes in the grid. The conditional model for the data, given the true temperature
and salinity, is described by: 
\begin{equation}\label{likelihood}
\by | \bxi \sim N( \bG \bxi, \bR), %\pi(\by | \bxi)= \frac{1}{(2\pi)^{m}|\bR|^{\frac{1}{2}}}e^{-\frac{1}{2}(\by -\bG\bxi)^T\bR^{-1}(\by-\bG\bxi)},
\end{equation}
where $\bG$ is a $2n_y \times 2n$ matrix containing '$1$'s on the
measurement indices of the grid and '$0$' otherwise. The size
$2n_y \times 2n_y$ covariance matrix $\bR$ contains \edcomment{zeroes except on the diagonal entries, which are set to $r^2_T$ and $r^2_S$, holding the measurement error variances of temperature and salinity observations}.

@@

In our application domain with the variables temperature and salinity,
the solutions to the complex integral equations for the expected IBV
are reduced to calculating bivariate and four-variate cumulative
distribution functions for Gaussian vectors. For the more general
case, one would be interested in $K$ random fields. In the ocean
sciences, the variables could include chlorophyll or other
bio-geochemical quantities in addition to temperature and salinity.

@@

The covariance is assumed to be stationary and separable for the two variables. 
The $2 \times 2$ pointwise covariance matrix is set to:
\begin{equation}\label{v0}
\bSigma(\bx)=\mbox{Var} 
\begin{bmatrix}
    \xi_T(\bx) \\
    \xi_S(\bx) 
    \end{bmatrix}=
\begin{bmatrix}
0.25^2 & 0.6 \cdot 0.25^2 \\
0.6 \cdot 0.25^2 & 0.25^2
\end{bmatrix}.
\end{equation}
The spatial correlation is of a Matern type \kc{cite or define}:
\begin{equation}\label{v}
\small
\mbox{Corr} 
\left(
\begin{bmatrix}
    \xi_T(\bx) \\
    \xi_S(\bx) 
    \end{bmatrix},
    \begin{bmatrix}
    \xi_T(\bx') \\
    \xi_S(\bx') 
    \end{bmatrix}
    \right)
    = \begin{bmatrix}
1 & 0.6  \\
0.6  & 1
\end{bmatrix}(1+\phi h)\exp (-\phi h),
\end{equation}
where $h=\sqrt{||\bx-\bx'||^2}$ and $\phi=0.3$ indicates an effective correlation range of about $1200$ m. 
%Figure \ref{fig:stat_design} shows the contour lines for the EP for the reference. We notice the trend of increasing salinity and temperature to the west.  
One realization of the random fields representing salinity and
temperature is shown in Fig. \ref{fig:true_temp} and
\ref{fig:true_sal}. The true ES is a realization from this model as shown
in Fig. \ref{fig:ESet}.

@@

For a fixed survey length, a closed form expression for the expected IBV is available as in Eq. \eqref{sur}. However, for the sequential approaches this is not the
case. For comparison the properties are therefore evaluated using
Monte Carlo sampling over several replicates of realizations from the model while conducting simulated sequential surveys for each
one. Fig. \ref{fig:Eprob} shows the conditional EP, given data
gathered along the north-south survey lines in these figures. In the
Monte Carlo replicates, such results are repeatedly computed to
approximate the expected IBV. We also compare predictive performance
measured by root mean square error (RMSE) for temperature and salinity
estimates \edcomment{as well as} also the variance reduction in these two variables. It is
important to note that the objective function used by the agent is
focused on reducing the expected IBV, but we nevertheless expect that
we will achieve good predictive performance for criteria such as RMSE
as well. Another non-statistical criteria that is important for
practical purposes is the computational time needed for the strategy,
as this will impact the performance for an embedded system.
